Children of Eden: A Theater Response

### 2009-12-29 great_works/film_sweetnothing.tex
Finished another film response, added some that I forgot to earlier

I have had some experience with American Sign Language, though not very much
with deaf culture.  I had some friends in high school who took ASL classes, and
I taught a deaf man the gospel on my mission through an interpeter.  I have
also watched my sister teach her young children sign language so they can
communicate before they are able to speak.  It was fascinating to me to see
more of a world I have only had very limited contact with.  It made me
appreciate more the struggles that parents go through in trying to raise their
children, especially when disabilities are involved.  And as I am fairly
recently married and my wife is expected our first child, it made me think
about what it will be like to try to raise a family, and made me grateful that
my wife and I are able to peacefully resolve our conflicts.

>>>>

I have had some experience with American Sign Language, though not very much
with deaf culture.  I had some friends in high school who took ASL classes, and
I taught a deaf man the gospel on my mission through an interpeter.  I have
also watched my sister teach her young children sign language so they can
communicate before they are able to speak.  It was fascinating to me to see
more of a world I have only had very limited contact with.  It made me
appreciate more the struggles that parents go through in trying to raise their
children, especially when disabilities are involved.  And as I am fairly
recently married and my wife is expecting our first child, it made me think
about what it will be like to try to raise a family, and made me grateful that
my wife and I are able to peacefully resolve our conflicts.
